Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-05 paper/ms.tex
figure renaming
update manuscript

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI~837: A Young Validated Planet in IC~2602
}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.79\textwidth]{f1.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Binning at 6-minute intervals
    yields the black points.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$. Brighter stars are larger.
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.44\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
    imaging were derived from point-source injection-recovery
    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
    \label{fig:speckle}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

@@

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
Siding Spring Observatory near Coonabarabran, Australia
\citep{gilbert_veloce_2018}.  Veloce's currently implemented Rosso
camera provides coverage from 600--950$\,$nm at a spectral resolution
of $\approx 80{,}000$.  Many of the exposures were taken in average or
poor seeing conditions, when fiber-to-fiber cross-contamination on the
IFU-style fiber feed is strongest.  To reduce the spectra to
velocities, we cross-correlated against a high S/N template of
$\delta$ Pavonis, because with spectral type G8 IV it was the closest
\tn\ analog available in the Veloce spectral database.  The velocity
RMS seen across each visit was hundreds of meters per second, likely
due to uncorrected fiber-to-fiber cross-contamination.  For analysis
purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:rvs}.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
    companions along the same line of sight (BEB scenarios).  Each
    constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9b.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9a.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Youth diagnostics.}
  {\it Top:} Rotation periods for \tn\ and selected open clusters.
  The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
  (1000$\,$Myr) are shown.  Their rotation periods were measured by
  \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
  open clusters.  The field star sample is drawn from Kepler planet
  hosts, and was measured by \citet{berger_identifying_2018} using
  Keck-HIRES.  The young open clusters members were surveyed by
  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
  lithium depletion boundary ages for these clusters of
  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
    \label{fig:lithium_rotation}
	}
\end{figure}

@@

A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
Chilean Ministry of Economy. A.J.\ acknowledges additional support
from FONDECYT project 1171208.  J.I.V\ acknowledges support from
CONICYT-PFCHA/Doctorado Nacional-21191829.  R.B.\ acknowledges support
from FONDECYT Post-doctoral Fellowship Project 3180246.
%
C.T.\ and C.B\ acknowledge support from Australian Research Council
grants LE150100087, LE160100014, LE180100165, DP170103491 and
DP190103688.
%
C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
Astronomy \& Astrophysics, funded through an endowment established by
the Dunlap family and the University of Toronto.
%
D.D.\ acknowledges support through the TESS Guest Investigator Program
Grant 80NSSC19K1727.

%
%
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

>>>>

\title{
  Cluster Difference Imaging Photometric Survey. II.
  TOI~837: A Young Validated Planet in IC~2602
}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.79\textwidth]{f1a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Binning at 6-minute intervals
    yields the black points.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$. Brighter stars are larger.
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.44\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
    imaging were derived from point-source injection-recovery
    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
    \label{fig:speckle}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

@@

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
Siding Spring Observatory near Coonabarabran, Australia
\citep{gilbert_veloce_2018}.  The currently operational
``Veloce-Rosso'' channel provides coverage from 600--950$\,$nm at a
spectral resolution of $\approx 80{,}000$.  Many of the exposures were
taken in average or poor seeing conditions, when the SNR is lowest and
the fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a template of $\delta$ Pavonis, because with spectral type G8
IV it was the closest high-SNR \tn\ analog available in the Veloce
spectral database.  The velocity RMS seen across each visit was
hundreds of meters per second, likely due to uncorrected
fiber-to-fiber cross-contamination.  This cross-contamination severely
affects the wavelength solutions for the 19 individual science fibres,
ultimately leading to significantly increased RV scatter. For analysis
purposes, we averaged the single-shot RVs across each visit, and set
the velocity uncertainties to be the standard deviation of the
per-visit exposures.  The velocities are given in Table~\ref{tab:rvs},
and shown in Figure~\ref{fig:rvs}.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
    companions along the same line of sight (BEB scenarios).  Each
    constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Youth diagnostics.}
  {\it Top:} Rotation periods for \tn\ and selected open clusters.
  The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
  (1000$\,$Myr) are shown.  Their rotation periods were measured by
  \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
  open clusters.  The field star sample is drawn from Kepler planet
  hosts, and was measured by \citet{berger_identifying_2018} using
  Keck-HIRES.  The young open clusters members were surveyed by
  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
  lithium depletion boundary ages for these clusters of
  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
    \label{fig:lithium_rotation}
	}
\end{figure}

@@

A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
Chilean Ministry of Economy. A.J.\ acknowledges additional support
from FONDECYT project 1171208.  J.I.V\ acknowledges support from
CONICYT-PFCHA/Doctorado Nacional-21191829.  R.B.\ acknowledges support
from FONDECYT Post-doctoral Fellowship Project 3180246.
%
C.T.\ and C.B\ acknowledge support from Australian Research Council
grants LE150100087, LE160100014, LE180100165, DP170103491 and
DP190103688.
%
C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
Astronomy \& Astrophysics, funded through an endowment established by
the Dunlap family and the University of Toronto.
%
D.D.\ acknowledges support through the TESS Guest Investigator Program
Grant 80NSSC19K1727.
%
%
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%
